\problemname{Doomsday Rule}
In 1973, mathmetician John Conway, invented an algorithm for quickly computing
the day of the week (e.g. Monday, Tuesday) from any date in history. The algorithm,
which he called the Doomsday algorithm, was designed to be simple enough to be
computed by hand.

Conway's algorithm hinges on the cyclic nature of the Gregorian calendar and consists
of three steps.
\begin{enumerate}
    \item Calculate the anchor day for a given century
    \item Calculate doomsday for the specific year. Certain dates (e.g. April 4th)
        in every month always occur on doomdays.
    \item Lastly, count (modulo 7) from the nearest doomsday to your desired day
\end{enumerate}

Days of the week are numbered from Sunday (with a value of $0$) through Saturday 
(with a value of $6$). The anchor day can be found using the formula:

\[a = (5\times(\lfloor{\dfrac{\text{yyyy}}{100}}\rfloor \text{ mod } 4) + 2) \text{ mod }7.\]

The doomsday can then be calculated using the formula:

\[d = ((y + \lfloor{\dfrac{y}{4}}\rfloor +  a) \text{ mod } 7\]

Where $y = \text{yyyy  mod } 100$

In every year, the following dates will occur on the doomsday:
\begin{itemize}
    \item January 3rd (which becomes January 4th in leap years)
    \item February 28th (which becomes February 29th in leap years)
    \item April 4th
    \item May 9th
    \item June 6th
    \item July 11th
    \item August 8th
    \item September 5th
    \item October 10th
    \item November 7th
    \item December 12th
\end{itemize}

Leap years occur if the year is evenly divisible by 4 but not 100. They
also occur in years divisible by 400. 2000 was a leap year, but 2200 will
be a common year.
\section*{Input}
The first line contains the number of test cases $1 \leq n \leq 10,000$ followed
by $n$ test cases, one per line. Each test case is in the format \textbf{dd month yyyy}
where $\text{month} \in \{$January, February, March, April, May, June, July, August,
September, October, November, December$\}$, $1 \leq \text{dd} \leq 31$, and $0 \leq
\text{yyyy} \leq 3,000$. All years are CE (AD) in the Gregorian Calendar and leading
zeroes won't be present.

For dates before the implementation of the Gregorian Calender, use the proleptic
Gregorian Calendar instead of the Julian Calendar. This way, Conway's Doomsday algorithm
applies consistently over all input dates.
\section*{Output}
Output the day of the week for each line of the input in the same order one
day per line. Day names are case-insensitive but abbreviations will not
be accepted.
